---
title: "Support for participating in outreach and the benefits of doing so"
author: "Achintya Rao"
date: "6 August 2016"
output:
    revealjs::revealjs_presentation:
        theme: serif
        highlight: pygments
        incremental: true
        center: true
        transition: slide
        reveal_options:
            slideNumber: true
        fig_caption: true
        showNotes: true
    html_document:
        dev: svg
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
dat <- read.csv(file = "../quant_analysis/final_dataset.csv", header = TRUE)
countries  <- read.csv(file = "data/countries.csv", header = TRUE)
library(dplyr)
library(plotly)
library(gridExtra)

# for long form conversion of data frame
library(reshape2)

likert_units <- seq(0.0000, 5.0000, by=1)
```

---

<section><h1>Conclusions</h1>

## Support for outreach participation

- High agreement that outreach is important because research is funded 
by taxpayers, and funding agencies should help scientists communicate 
research to wider audiences.
- However, few scientists feel outreach plans should be a component of 
grant applications.

## Benefits of outreach participation

- High agreement that it makes one a better scientist, gives one a sense of 
enjoyment and gives job satisfaction.
- Few feel that it attracts research funding, advances one's career, 
provides collaboration opportunities or makes one think about one's research 
in new ways.

</section>

---

<section><h1>A bit about me</h1>

##

> - **Science Communicator** (2010 &mdash; present)<br />Compact Muon Solenoid
(CMS) Collaboration at CERN
> - **Doctoral Student** (2014 &mdash; present)<br />UWE Science Communication
Unit, Bristol
>     - **MA in Science Journalism** (2009 &mdash; 2010)<br />City University,
London
>     - **BSc in Physics** (2005 &mdash; 2008)<br />St. Xavier’s College,
Mumbai (Bombay)

<br />
<br />
<small>
Twitter: [\@RaoOfPhysics](https://twitter.com/RaoOfPhysics) |
GitHub: [\@RaoOfPhysics](https://github.com/RaoOfPhysics)<br />
This presentation: [github.com/RaoOfPhysics/201608_ICHEP](https://github.com/RaoOfPhysics/201608_ICHEP)
</small>

</section>

---

<section><h1>Science Communication: Evolving Views</h1>

## Scientific Literacy

“greater knowledge about the facts of science will  improve people’s lives while gaining public support for, and reducing opposition to, research”

##  Public Understanding of Science and Technology

> “part of each scientist’s professional responsibility  to promote the public understanding of science”

&mdash; The Royal Society, 1985, p.24

## The Deficit Model

“the role of scientists and science communicators is to fill a perceived knowledge deficit among the public”

## Low levels of Scientific Literacy

> “Many [scientists] recognise, in their own inability to be certain of their answers, that the public cannot be expected to retain  facts that are not useful.”

&mdash; Stocklmayer & Bryant, 2012, p.18

</section>

---

<section><h1>Public Engagement with Science and Technology</h1>

## 

> “while scientists may have scientific facts at their disposal, the members of the public concerned have local knowledge and an understanding of, and personal interest in, the problems to be solved”

&mdash; Miller, 2001, p.117

## Three aspects/stages:

> 1. “scientists […] encouraged to inform the public”
> 2. “scientists […] encouraged to develop dialogue on scientific facts and processes”
> 3. “scientists must engage with society in the early phase of scientific development”

&mdash; Crettaz von Roten, 2011, p.54

## Science Communication research

- Conversation dominated with research fields that have:
    - direct impact
    - immediate impact

- What about fundamental research?

</section>

---

<section><h1>My PhD project</h1>

## "Engagement" &rarr; "Outreach"

- used to refer to all science-communication activities
“designed for an audience outside academia” (Crettaz&nbsp;von&nbsp;Roten, 2011, p.54)
- used among particle physicists to refer to:
    - working with schools
    - direct dialogue with the public
    - disseminating information through the media

##

> The term “outreach” refers to all science communication and education
activities that bring scientific research to audiences outside
the research community. It is also known as “popularisation”.

&mdash; note included in survey

## Research questions

- What are the attitudes towards outreach within the particle-physics
community and what are the motivations for and barriers against participating
- Do these vary w.r.t.
age, gender and academic position

## Research questions (…)

- How are these influenced by
    - funding bodies
    - national expectations towards outreach
    - the multicultural nature of international collaborations
- How does the community perceive the usefulness and impact of outreach

</section>

---

<section data-background="images/1205187_03-A4-at-144-dpi.jpg">

##

### [CERN](http://home.cern)

The European Laboratory for Particle Physics

- Geneva, Switzerland
- host laboratory for international collaborations
- ~half of all 20,000 particle physicists

</section>

<section data-background="images/0910152_02-A4-at-144-dpi.jpg">

</section>

<section data-background="images/0807031_01-A4-at-144-dpi.jpg">

</section>

<section data-background="images/IMG_9286.JPG">

##

### The CMS Collaboration

[**C**ompact **M**uon **S**olenoid](http://cms.web.cern.ch)

- one of the two teams that [discovered the Higgs boson in 2012](http://cms.web.cern.ch/news/observation-new-particle-mass-125-gev)
- people (June 2015)
    - over 4000 physicists, engineers, students  (not including technicians
        and admin)
    - 183 institutes, universities, laboratories from 42 countries
    - 80+ nationalities

</section>

---

<section><h1>Data collection for quantitative analysis</h1>

## Electronic survey distributed by e-mail

- Sent to the whole collaboration via mailing list
- Three reminders sent to whole list
- Engineers reminded separately as well
- Representatives from low-response countries reminded separately

## Responses

- over 400, but a few duplicates
- final count: **391** valid responses
- ~10% of the collaboration

## CMS member countries

```{r}
# Code below by Rik Smith-Unna (@Blahah on GitHub)

# precompute the plot variable - this is required because we'll
# need to 'melt' the dataframe into long format, which will
# mix values from different variables in a column
countries$Country_Response_pc <-
    countries$Country_Response / countries$Country_Total * 100

# Some R wizardry I have yet to understand - Achintya
countries$Country <- factor(
    countries$Country,
    levels=arrange(countries, -Country_Response)$Country
    )

# select only the columns we need, then reshape
# the data frame by 'melting' it to long form.
# we only have one 'id variable' - country, so
# all the other variables will be collapsed
# into just two columns: variable and value
# we go from one row per country, to one row per value per country
# this is the format ggplot always uses - and it's super powerful
countries_long <- melt(
    countries[, c('Country', 'Country_Response', 'Country_Response_pc')],
    id=c('Country')
    )

# now just set x as country, but colour bars by another variable
p <- ggplot(countries_long, aes(x=Country, y=value, fill=variable)) +
    # we also need to specify that we want to use the values,
    # rather than the number of occurences, as the bar size
    # and that we want the bars side by side 'dodge' rather than
    # stacked
    geom_bar(stat='identity', position=position_dodge(), color="white") +
        coord_cartesian(ylim=c(0, 50))

ggplotly()

```
</section>

---

<section><h1>Participation in outreach</h1>

## 

```{r}
ggplot(dat, aes(x = previous_participation)) +
    geom_bar(width=0.8) +
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) + 
    facet_wrap(~gender) +
    ylab("Count") + 
    theme(axis.title.x=element_blank()) +
    labs(title ="“Have you previously participated in outreach activities?”")
```

</section>

---

<section><h1>Support for outreach participation</h1>

##

```{r}
imp_because_taxes <- melt(as.matrix(dat[c('imp_because_taxes')]))
imp_because_taxes$value <- factor(imp_because_taxes$value, 
                                  levels=c(1, 2, 3, 4, 5))

ggplot(imp_because_taxes, aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    labs(title = "“It is important for scientists to take part in outreach activities \nbecause taxes from citizens fund research.”")
```

*… outreach is important because research is supported by taxes…*

##

```{r}
funding_should_support <- melt(as.matrix(dat[c('funding_should_support')]))
funding_should_support$value <- factor(funding_should_support$value, 
                                       levels=c(1, 2, 3, 4, 5))

ggplot(funding_should_support, aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    labs(title = "“Funding bodies should provide support for scientists \nto communicate their research to the non-specialist public.”")
```

*… funding bodies should scientists help do outreach…*

##

```{r}
grants_wider_society <- melt(as.matrix(dat[c('grants_wider_society')]))
grants_wider_society$value <- factor(grants_wider_society$value, 
                                     levels=c(1, 2, 3, 4, 5))

ggplot(grants_wider_society, aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    labs(title = "“When applying for grants, scientists should be required to provide details \non how their research will be communicated to the wider society.”")
```

*… outreach details included in grant applications…*

##

<?xml version="1.0" encoding="UTF-8" standalone="no"?>
<svg
   xmlns:dc="http://purl.org/dc/elements/1.1/"
   xmlns:cc="http://creativecommons.org/ns#"
   xmlns:rdf="http://www.w3.org/1999/02/22-rdf-syntax-ns#"
   xmlns:svg="http://www.w3.org/2000/svg"
   xmlns="http://www.w3.org/2000/svg"
   xmlns:sodipodi="http://sodipodi.sourceforge.net/DTD/sodipodi-0.dtd"
   xmlns:inkscape="http://www.inkscape.org/namespaces/inkscape"
   version="1.1"
   height="620"
   width="900"
   id="svg2"
   inkscape:version="0.91 r13725"
   sodipodi:docname="imp_because_taxes_vs_funding_should_support.svg">
  <metadata
     id="metadata140">
    <rdf:RDF>
      <cc:Work
         rdf:about="">
        <dc:format>image/svg+xml</dc:format>
        <dc:type
           rdf:resource="http://purl.org/dc/dcmitype/StillImage" />
        <dc:title></dc:title>
      </cc:Work>
    </rdf:RDF>
  </metadata>
  <defs
     id="defs138" />
  <sodipodi:namedview
     pagecolor="#ffffff"
     bordercolor="#666666"
     borderopacity="1"
     objecttolerance="10"
     gridtolerance="10"
     guidetolerance="10"
     inkscape:pageopacity="0"
     inkscape:pageshadow="2"
     inkscape:window-width="1916"
     inkscape:window-height="1035"
     id="namedview136"
     showgrid="false"
     showguides="true"
     inkscape:guide-bbox="true"
     inkscape:zoom="1.0960155"
     inkscape:cx="390.47534"
     inkscape:cy="332.99167"
     inkscape:window-x="4"
     inkscape:window-y="23"
     inkscape:window-maximized="1"
     inkscape:current-layer="svg2" />
  <g
     transform="translate(50,62)"
     id="g4">
    <g
       id="g6">
      <path
         style="fill:none;stroke:#ae69bf;stroke-width:117.64700317;stroke-opacity:0.4"
         d="m 10,441.17647 c 390,0 390,0 780,0"
         class="link"
         id="path8"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#698bbf;stroke-width:101.1760025;stroke-opacity:0.4"
         d="m 10,227.64706 c 390,0 390,7.05882 780,7.05882"
         class="link"
         id="path10"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#698bbf;stroke-width:40;stroke-opacity:0.4"
         d="m 10,298.23529 c 390,0 390,64.11765 780,64.11765"
         class="link"
         id="path12"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#69bf8b;stroke-width:34.11759949;stroke-opacity:0.4"
         d="m 10,112.35294 c 390,0 390,54.70588 780,54.70588"
         class="link"
         id="path14"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#ae69bf;stroke-width:30.58819962;stroke-opacity:0.4"
         d="m 10,367.05882 c 390,0 390,-66.47058 780,-66.47058"
         class="link"
         id="path16"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#69bf8b;stroke-width:28.23530006;stroke-opacity:0.4"
         d="m 10,81.176471 c 390,0 390,-7.058824 780,-7.058824"
         class="link"
         id="path18"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#698bbf;stroke-width:21.17650032;stroke-opacity:0.4"
         d="m 10,166.47059 c 390,0 390,-67.647061 780,-67.647061"
         class="link"
         id="path20"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#ae69bf;stroke-width:17.64710045;stroke-opacity:0.4"
         d="m 10,342.94118 c 390,0 390,-224.70589 780,-224.70589"
         class="link"
         id="path22"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#aebf69;stroke-width:11.76469994;stroke-opacity:0.4"
         d="m 10,42.941176 c 390,0 390,101.176474 780,101.176474"
         class="link"
         id="path24"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#69bf8b;stroke-width:10.58819962;stroke-opacity:0.4"
         d="m 10,134.70588 c 390,0 390,202.35294 780,202.35294"
         class="link"
         id="path26"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bf6969;stroke-width:5.88234997;stroke-opacity:0.4"
         d="m 10,7.6470588 c 390,0 390,43.5294122 780,43.5294122"
         class="link"
         id="path28"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#aebf69;stroke-width:5.88234997;stroke-opacity:0.4"
         d="m 10,34.117647 c 390,0 390,22.941177 780,22.941177"
         class="link"
         id="path30"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#69bf8b;stroke-width:5.88234997;stroke-opacity:0.4"
         d="m 10,64.117647 c 390,0 390,-38.235294 780,-38.235294"
         class="link"
         id="path32"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#698bbf;stroke-width:5.88234997;stroke-opacity:0.4"
         d="m 10,152.94118 c 390,0 390,-121.176474 780,-121.176474"
         class="link"
         id="path34"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bf6969;stroke-width:3.52940989;stroke-opacity:0.4"
         d="m 10,1.7647059 c 390,0 390,0 780,0"
         class="link"
         id="path36"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bf6969;stroke-width:3.52940989;stroke-opacity:0.4"
         d="m 10,13.529412 c 390,0 390,314.117648 780,314.117648"
         class="link"
         id="path38"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#aebf69;stroke-width:3.52940989;stroke-opacity:0.4"
         d="m 10,29.411765 c 390,0 390,-8.235294 780,-8.235294"
         class="link"
         id="path40"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#ae69bf;stroke-width:3.52940989;stroke-opacity:0.4"
         d="m 10,332.35294 c 390,0 390,-295.882352 780,-295.882352"
         class="link"
         id="path42"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#aebf69;stroke-width:2.35294008;stroke-opacity:0.4"
         d="m 10,26.470588 c 390,0 390,-21.7647056 780,-21.7647056"
         class="link"
         id="path44"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#aebf69;stroke-width:2.35294008;stroke-opacity:0.4"
         d="m 10,50 c 390,0 390,280.58824 780,280.58824"
         class="link"
         id="path46"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#ae69bf;stroke-width:2.35294008;stroke-opacity:0.4"
         d="m 10,329.41176 c 390,0 390,-322.3529365 780,-322.3529365"
         class="link"
         id="path48"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bf6969;stroke-width:1.17647004;stroke-opacity:0.4"
         d="m 10,4.1176471 c 390,0 390,14.7058819 780,14.7058819"
         class="link"
         id="path50"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bf6969;stroke-width:1.17647004;stroke-opacity:0.4"
         d="m 10,11.176471 c 390,0 390,126.470589 780,126.470589"
         class="link"
         id="path52"
         inkscape:connector-curvature="0" />
    </g>
    <g
       id="g54">
      <g
         transform="translate(790,0)"
         class="node"
         id="g56">
        <rect style="fill:#666666" width="10" height="8.2352943" id="rect58" x="0" y="0"><title id="title60">1<br />7</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:end"
           dy="0"
           y="4.1176472"
           x="-6"
           id="text62">1</text>
      </g>
      <g
         transform="translate(790,18.235294)"
         class="node"
         id="g64">
        <rect style="fill:#666666" width="10" height="20" id="rect66" x="0" y="0"><title id="title68">2<br />17</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:end"
           dy="0"
           y="10"
           x="-6"
           id="text70">2</text>
      </g>
      <g
         transform="translate(790,48.235294)"
         class="node"
         id="g72">
        <rect style="fill:#666666" width="10" height="78.823532" id="rect74" x="0" y="0"><title id="title76">3<br />67</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:end"
           dy="0"
           y="39.411766"
           x="-6"
           id="text78">3</text>
      </g>
      <g
         transform="translate(790,137.05882)"
         class="node"
         id="g80">
        <rect style="fill:#666666" width="10" height="178.82353" id="rect82" x="0" y="0"><title id="title84">4<br />152</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:end"
           dy="0"
           y="89.411766"
           x="-6"
           id="text86">4</text>
      </g>
      <g
         transform="translate(790,325.88235)"
         class="node"
         id="g88">
        <rect style="fill:#666666" width="10" height="174.11765" id="rect90" x="0" y="0"><title id="title92">5<br />148</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:end"
           dy="0"
           y="87.058823"
           x="-6"
           id="text94">5</text>
      </g>
      <g
         class="node"
         id="g96">
        <rect width="10" height="15.294118" id="rect98" x="0" y="0"><title id="title100">1<br />13</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:start"
           dy="0"
           y="7.647059"
           x="16"
           id="text102">1</text>
      </g>
      <g
         transform="translate(0,25.294118)"
         class="node"
         id="g104">
        <rect width="10" height="25.882353" id="rect106" x="0" y="0"><title id="title108">2<br />22</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:start"
           dy="0"
           y="12.941176"
           x="16"
           id="text110">2</text>
      </g>
      <g
         transform="translate(0,61.176471)"
         class="node"
         id="g112">
        <rect width="10" height="78.823532" id="rect114" x="0" y="0"><title id="title116">3<br />67</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:start"
           dy="0"
           y="39.411766"
           x="16"
           id="text118">3</text>
      </g>
      <g
         transform="translate(0,150)"
         class="node"
         id="g120">
        <rect width="10" height="168.23529" id="rect122" x="0" y="0"><title id="title124">4<br />143</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:start"
           dy="0"
           y="84.117645"
           x="16"
           id="text126">4</text>
      </g>
      <g
         transform="translate(0,328.23529)"
         class="node"
         id="g128">
        <rect width="10" height="171.76471" id="rect130" x="0" y="0"><title id="title132">5<br />146</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:start"
           dy="0"
           y="85.882355"
           x="16"
           id="text134">5</text>
      </g>
    </g>
  </g>
  <text
     xml:space="preserve"
     style="font-style:normal;font-weight:normal;font-size:40px;line-height:125%;font-family:sans-serif;letter-spacing:0px;word-spacing:0px;fill:#000000;fill-opacity:1;stroke:none;stroke-width:1px;stroke-linecap:butt;stroke-linejoin:miter;stroke-opacity:1"
     x="202.40361"
     y="31.504679"
     id="text4270"
     sodipodi:linespacing="125%"><tspan
       sodipodi:role="line"
       id="tspan4272"
       x="202.40361"
       y="31.504679"
       style="font-size:12.5px;text-align:center;text-anchor:middle">“It is important for scientists to take part in outreach activities</tspan><tspan
       sodipodi:role="line"
       x="202.40361"
       y="47.129677"
       style="font-size:12.5px;text-align:center;text-anchor:middle"
       id="tspan4274">because taxes from citizens fund research.”</tspan></text>
  <text
     xml:space="preserve"
     style="font-style:normal;font-weight:normal;font-size:12.5px;line-height:125%;font-family:sans-serif;letter-spacing:0px;word-spacing:0px;fill:#000000;fill-opacity:1;stroke:none;stroke-width:1px;stroke-linecap:butt;stroke-linejoin:miter;stroke-opacity:1"
     x="704.89557"
     y="583.50415"
     id="text4276"
     sodipodi:linespacing="125%"><tspan
       sodipodi:role="line"
       id="tspan4278"
       x="704.89557"
       y="583.50415"
       style="text-align:center;text-anchor:middle">“Funding bodies should provide support for scientists</tspan><tspan
       sodipodi:role="line"
       x="704.89557"
       y="599.12915"
       id="tspan4280"
       style="text-align:center;text-anchor:middle">to communicate their research to the non-specialist public.”</tspan></text>
</svg>

</section>

---

<section><h1>Benefits of outreach participation</h1>

##

```{r}
makes_better_scientist <- melt(as.matrix(dat[c('makes_better_scientist')]))
makes_better_scientist$value <- factor(makes_better_scientist$value, 
                                       levels=c(1, 2, 3, 4, 5))

ggplot(na.omit(makes_better_scientist), aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    labs(title = "“[Participating in outreach] makes me a better scientist.”")
```

*… makes me a better scientist…*

##

```{r}
feeling_enjoyment <- melt(as.matrix(dat[c('feeling_enjoyment')]))
feeling_enjoyment$value <- factor(feeling_enjoyment$value, 
                                  levels=c(1, 2, 3, 4, 5))

ggplot(na.omit(feeling_enjoyment), aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    labs(title = "“I get a feeling of enjoyment [from participating in outreach].”")
```

*… feeling of enjoyment…*

##

```{r}
job_satisfaction <- melt(as.matrix(dat[c('job_satisfaction')]))
job_satisfaction$value <- factor(job_satisfaction$value, 
                                 levels=c(1, 2, 3, 4, 5))

ggplot(na.omit(job_satisfaction), aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    labs(title = "“[Participating in outreach] gives me job satisfaction.”")
```

*… job satisfaction…*

##

<?xml version="1.0" encoding="UTF-8" standalone="no"?>
<svg
   xmlns:dc="http://purl.org/dc/elements/1.1/"
   xmlns:cc="http://creativecommons.org/ns#"
   xmlns:rdf="http://www.w3.org/1999/02/22-rdf-syntax-ns#"
   xmlns:svg="http://www.w3.org/2000/svg"
   xmlns="http://www.w3.org/2000/svg"
   xmlns:sodipodi="http://sodipodi.sourceforge.net/DTD/sodipodi-0.dtd"
   xmlns:inkscape="http://www.inkscape.org/namespaces/inkscape"
   version="1.1"
   height="620"
   width="900"
   id="svg2"
   inkscape:version="0.91 r13725"
   sodipodi:docname="feeling_enjoyment_vs_job_satisfaction.svg">
  <metadata
     id="metadata162">
    <rdf:RDF>
      <cc:Work
         rdf:about="">
        <dc:format>image/svg+xml</dc:format>
        <dc:type
           rdf:resource="http://purl.org/dc/dcmitype/StillImage" />
        <dc:title></dc:title>
      </cc:Work>
    </rdf:RDF>
  </metadata>
  <defs
     id="defs160" />
  <sodipodi:namedview
     pagecolor="#ffffff"
     bordercolor="#666666"
     borderopacity="1"
     objecttolerance="10"
     gridtolerance="10"
     guidetolerance="10"
     inkscape:pageopacity="0"
     inkscape:pageshadow="2"
     inkscape:window-width="1916"
     inkscape:window-height="1035"
     id="namedview158"
     showgrid="false"
     inkscape:zoom="1.0960155"
     inkscape:cx="400"
     inkscape:cy="260"
     inkscape:window-x="4"
     inkscape:window-y="23"
     inkscape:window-maximized="1"
     inkscape:current-layer="svg2" />
  <g
     transform="translate(50.181772,59.64302)"
     id="g4">
    <g
       id="g6">
      <path
         style="fill:none;stroke:#6969bf;stroke-width:133.5039978;stroke-opacity:0.4"
         d="m 10,418.6445 c 390,0 390,1.1509 780,1.1509"
         class="link"
         id="path8"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#69bfbf;stroke-width:121.99500275;stroke-opacity:0.4"
         d="m 10,216.44501 c 390,0 390,2.30179 780,2.30179"
         class="link"
         id="path10"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#6969bf;stroke-width:40.28129959;stroke-opacity:0.4"
         d="m 10,331.75192 c 390,0 390,-31.86701 780,-31.86701"
         class="link"
         id="path12"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#69bf69;stroke-width:36.82860184;stroke-opacity:0.4"
         d="m 10,82.148338 c 390,0 390,4.60358 780,4.60358"
         class="link"
         id="path14"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#69bfbf;stroke-width:24.16880035;stroke-opacity:0.4"
         d="m 10,143.36317 c 390,0 390,-26.11253 780,-26.11253"
         class="link"
         id="path16"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#69bfbf;stroke-width:19.56520081;stroke-opacity:0.4"
         d="m 10,287.22506 c 390,0 390,56.03581 780,56.03581"
         class="link"
         id="path18"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#69bf69;stroke-width:12.65979958;stroke-opacity:0.4"
         d="m 10,106.89258 c 390,0 390,44.52686 780,44.52686"
         class="link"
         id="path20"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bf6969;stroke-width:10.35809994;stroke-opacity:0.4"
         d="m 10,5.1790281 c 390,0 390,0 780,0"
         class="link"
         id="path22"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bfbf69;stroke-width:9.20716;stroke-opacity:0.4"
         d="m 10,31.867008 c 390,0 390,-2.301791 780,-2.301791"
         class="link"
         id="path24"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#69bf69;stroke-width:8.05626965;stroke-opacity:0.4"
         d="m 10,59.705882 c 390,0 390,-21.508951 780,-21.508951"
         class="link"
         id="path26"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bfbf69;stroke-width:6.90537024;stroke-opacity:0.4"
         d="m 10,39.923274 c 390,0 390,24.961636 780,24.961636"
         class="link"
         id="path28"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#69bfbf;stroke-width:4.60358;stroke-opacity:0.4"
         d="m 10,128.97698 c 390,0 390,-84.450126 780,-84.450126"
         class="link"
         id="path30"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bf6969;stroke-width:3.45268989;stroke-opacity:0.4"
         d="m 10,12.084399 c 390,0 390,47.621483 780,47.621483"
         class="link"
         id="path32"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#69bf69;stroke-width:2.30179;stroke-opacity:0.4"
         d="m 10,114.3734 c 390,0 390,217.95397 780,217.95397"
         class="link"
         id="path34"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#6969bf;stroke-width:2.30179;stroke-opacity:0.4"
         d="m 10,310.46036 c 390,0 390,-179.97443 780,-179.97443"
         class="link"
         id="path36"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bf69bf;stroke-width:2.30179;stroke-opacity:0.4"
         d="m 10,498.8491 c 390,0 390,0 780,0"
         class="link"
         id="path38"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bf6969;stroke-width:1.15090001;stroke-opacity:0.4"
         d="m 10,14.386189 c 390,0 390,128.976981 780,128.976981"
         class="link"
         id="path40"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bf6969;stroke-width:1.15090001;stroke-opacity:0.4"
         d="m 10,15.537084 c 390,0 390,315.063936 780,315.063936"
         class="link"
         id="path42"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bfbf69;stroke-width:1.15090001;stroke-opacity:0.4"
         d="m 10,26.68798 c 390,0 390,-15.754476 780,-15.754476"
         class="link"
         id="path44"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bfbf69;stroke-width:1.15090001;stroke-opacity:0.4"
         d="m 10,43.951407 c 390,0 390,100.562663 780,100.562663"
         class="link"
         id="path46"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#69bf69;stroke-width:1.15090001;stroke-opacity:0.4"
         d="m 10,55.102302 c 390,0 390,-43.017903 780,-43.017903"
         class="link"
         id="path48"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#69bfbf;stroke-width:1.15090001;stroke-opacity:0.4"
         d="m 10,126.09974 c 390,0 390,-112.864446 780,-112.864446"
         class="link"
         id="path50"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#6969bf;stroke-width:1.15090001;stroke-opacity:0.4"
         d="m 10,307.58312 c 390,0 390,-293.196931 780,-293.196931"
         class="link"
         id="path52"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#6969bf;stroke-width:1.15090001;stroke-opacity:0.4"
         d="m 10,308.73402 c 390,0 390,-261.329928 780,-261.329928"
         class="link"
         id="path54"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#6969bf;stroke-width:1.15090001;stroke-opacity:0.4"
         d="m 10,485.97187 c 390,0 390,11.15089 780,11.15089"
         class="link"
         id="path56"
         inkscape:connector-curvature="0" />
      <path
         style="fill:none;stroke:#bf69bf;stroke-width:1.15090001;stroke-opacity:0.4"
         d="m 10,497.12276 c 390,0 390,-364.91048 780,-364.91048"
         class="link"
         id="path58"
         inkscape:connector-curvature="0" />
    </g>
    <g
       id="g60">
      <g
         class="node"
         id="g62">
        <rect width="10" height="16.112532" id="rect64" x="0" y="0"><title id="title66">1<br />14</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:start"
           dy="0"
           y="8.0562658"
           x="16"
           id="text68">1</text>
      </g>
      <g
         transform="translate(0,26.112532)"
         class="node"
         id="g70">
        <rect width="10" height="18.414322" id="rect72" x="0" y="0"> <title id="title74">2<br />16</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:start"
           dy="0"
           y="9.2071609"
           x="16"
           id="text76">2</text>
      </g>
      <g
         transform="translate(0,54.526854)"
         class="node"
         id="g78">
        <rect width="10" height="60.997444" id="rect80" x="0" y="0"><title id="title82">3<br />53</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:start"
           dy="0"
           y="30.498722"
           x="16"
           id="text84">3</text>
      </g>
      <g
         transform="translate(0,125.5243)"
         class="node"
         id="g86">
        <rect width="10" height="171.48338" id="rect88" x="0" y="0"><title id="title90">4<br />149</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:start"
           dy="0"
           y="85.741692"
           x="16"
           id="text92">4</text>
      </g>
      <g
         transform="translate(0,307.00767)"
         class="node"
         id="g94">
        <rect width="10" height="179.53964" id="rect96" x="0" y="0"><title id="title98">5<br />156</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:start"
           dy="0"
           y="89.769821"
           x="16"
           id="text100">5</text>
      </g>
      <g
         transform="translate(0,496.54731)"
         class="node"
         id="g102">
        <rect width="10" height="3.4526854" id="rect104" x="0" y="0"><title id="title106">NA<br />3</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:start"
           dy="0"
           y="1.7263427"
           x="16"
           id="text108">NA</text>
      </g>
      <g
         transform="translate(790,0)"
         class="node"
         id="g110">
        <rect style="fill:#666666" width="10" height="14.961637" id="rect112" x="0" y="0"><title id="title114">1<br />13</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:end"
           dy="0"
           y="7.4808183"
           x="-6"
           id="text116">1</text>
      </g>
      <g
         transform="translate(790,24.961637)"
         class="node"
         id="g118">
        <rect style="fill:#666666" width="10" height="23.017902" id="rect120" x="0" y="0"><title id="title122">2<br />20</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:end"
           dy="0"
           y="11.508951"
           x="-6"
           id="text124">2</text>
      </g>
      <g
         transform="translate(790,57.97954)"
         class="node"
         id="g126">
        <rect style="fill:#666666" width="10" height="74.808182" id="rect128" x="0" y="0"><title id="title130">3<br />65</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:end"
           dy="0"
           y="37.404091"
           x="-6"
           id="text132">3</text>
      </g>
      <g
         transform="translate(790,142.78772)"
         class="node"
         id="g134">
        <rect style="fill:#666666" width="10" height="177.23785" id="rect136" x="0" y="0"><title id="title138">4<br />154</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:end"
           dy="0"
           y="88.618927"
           x="-6"
           id="text140">4</text>
      </g>
      <g
         transform="translate(790,330.02558)"
         class="node"
         id="g142">
        <rect style="fill:#666666" width="10" height="156.52174" id="rect144" x="0" y="0"><title id="title146">5<br />136</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:end"
           dy="0"
           y="78.260872"
           x="-6"
           id="text148">5</text>
      </g>
      <g
         transform="translate(790,496.54731)"
         class="node"
         id="g150">
        <rect style="fill:#666666" width="10" height="3.4526854" id="rect152" x="0" y="0"> <title id="title154">NA<br />3</title></rect>
        <text
           style="font-size:11px;font-family:Arial, Helvetica;text-anchor:end"
           dy="0"
           y="1.7263427"
           x="-6"
           id="text156">NA</text>
      </g>
    </g>
  </g>
  <text
     xml:space="preserve"
     style="font-style:normal;font-weight:normal;font-size:12.5px;line-height:125%;font-family:sans-serif;letter-spacing:0px;word-spacing:0px;fill:#000000;fill-opacity:1;stroke:none;stroke-width:1px;stroke-linecap:butt;stroke-linejoin:miter;stroke-opacity:1"
     x="120.93041"
     y="27.679886"
     id="text4290"
     sodipodi:linespacing="125%"><tspan
       sodipodi:role="line"
       x="122.92016"
       y="27.679886"
       id="tspan4294"
       style="text-align:center;text-anchor:middle">“I get a feeling of enjoyment </tspan><tspan
       sodipodi:role="line"
       x="120.93041"
       y="43.304886"
       style="text-align:center;text-anchor:middle"
       id="tspan4304">[from participating in outreach].”</tspan></text>
  <text
     xml:space="preserve"
     style="font-style:normal;font-weight:normal;font-size:12.5px;line-height:125%;font-family:sans-serif;letter-spacing:0px;word-spacing:0px;fill:#000000;fill-opacity:1;stroke:none;stroke-width:1px;stroke-linecap:butt;stroke-linejoin:miter;stroke-opacity:1"
     x="797.91431"
     y="583.50415"
     id="text4296"
     sodipodi:linespacing="125%"><tspan
       sodipodi:role="line"
       id="tspan4298"
       x="799.90405"
       y="583.50415"
       style="text-align:center;text-anchor:middle">“[Participating in outreach] </tspan><tspan
       sodipodi:role="line"
       x="797.91431"
       y="599.12915"
       id="tspan4300"
       style="text-align:center;text-anchor:middle">gives me job satisfaction.”</tspan></text>
</svg>

##

```{r}
attracts_funding <- melt(as.matrix(dat[c('attracts_funding')]))
attracts_funding$value <- factor(attracts_funding$value, 
                                 levels=c(1, 2, 3, 4, 5))

ggplot(na.omit(attracts_funding), aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    labs(title = "“[Participating in outreach] attracts research funding.”")
```

*… attracts research funding…*

##

```{r}
advances_career <- melt(as.matrix(dat[c('advances_career')]))
advances_career$value <- factor(advances_career$value, 
                                levels=c(1, 2, 3, 4, 5))

ggplot(na.omit(advances_career), aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    labs(title = "“[Participating in outreach] advances my career.”")
```

*… advances my career…*

##

```{r}
collaboration_opportunities <-
    melt(as.matrix(dat[c('collaboration_opportunities')]))
collaboration_opportunities$value <- factor(collaboration_opportunities$value, 
                                            levels=c(1, 2, 3, 4, 5))

ggplot(na.omit(collaboration_opportunities), aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    labs(title = "“[Participating in outreach] is an opportunity for others \nto contact me for collaborative purposes.”")
```

*… collaboration opportunities…*

##

```{r}
research_new_ways <- melt(as.matrix(dat[c('research_new_ways')]))
research_new_ways$value <- factor(research_new_ways$value, 
                                  levels=c(1, 2, 3, 4, 5))

ggplot(na.omit(research_new_ways), aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    labs(title = "“[Participating in outreach] shapes the direction of my research \nand makes me think about it in new ways.”")
```

*… think of my research in new ways…*

</section>

---

<section><h1>Conclusions</h1>

## Support for outreach participation

- High agreement that outreach is important because research is funded 
by taxpayers, and funding agencies should help scientists communicate 
research to wider audiences.
- However, few scientists feel outreach plans should be a component of 
grant applications.

## Benefits of outreach participation

- High agreement that it makes one a better scientist, gives one a sense of 
enjoyment and gives job satisfaction.
- Few feel that it attracts research funding, advances one's career, 
provides collaboration opportunities or makes one think about one's research 
in new ways.

</section>

---

<section><h1>Acknowledgements</h1>

##

Emma Weitkamp, Clare Wilkinson, Erik Stengler, Christine Sutton, for supervising my research

Achille Petrilli, CMS Head of Communications, for supporting my research

Special thanks to Richard Smith-Unna (t: [\@blahah404](https://twitter.com/blahah404)) for help with R code!

##

[R](https://www.r-project.org/) + [RStudio](https://www.rstudio.com/)

[reveal.js](http://lab.hakim.se/reveal-js/)

[plotly](https://plot.ly/)

[RAW](http://raw.densitydesign.org/)

[Git](https://git-scm.com/) + [GitHub](https://github.com/)

</section>

# Thank you