---
title: "Support for participating in outreach and the benefits of doing so"
author: "Achintya Rao"
date: "6 August 2016"
output:
    revealjs::revealjs_presentation:
        theme: serif
        highlight: pygments
        incremental: true
        center: true
        transition: slide
        reveal_options:
            slideNumber: true
        fig_caption: true
        showNotes: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
dat <- read.csv(file = "../quant_analysis/final_dataset.csv", header = TRUE)
countries  <- read.csv(file = "data/countries.csv", header = TRUE)
library(dplyr)
library(plotly)
library(gridExtra)

# for long form conversion of data frame
library(reshape2)

likert_units <- seq(0.0000, 5.0000, by=1)
```

---

<section><h1>Conclusions</h1>

## CONCLUSIONS 1

## CONCLUSIONS 2

</section>

---

<section><h1>A bit about me</h1>

##

> - **Science Communicator** (2010 &mdash; present)<br />Compact Muon Solenoid
(CMS) Collaboration at CERN
> - **Doctoral Student** (2014 &mdash; present)<br />UWE Science Communication
Unit, Bristol
>     - **MA in Science Journalism** (2009 &mdash; 2010)<br />City University,
London
>     - **BSc in Physics** (2005 &mdash; 2008)<br />St. Xavier’s College,
Mumbai (Bombay)

<br />
<br />
<small>
Twitter: [\@RaoOfPhysics](https://twitter.com/RaoOfPhysics) |
GitHub: [\@RaoOfPhysics](https://github.com/RaoOfPhysics)<br />
This presentation: [github.com/RaoOfPhysics/201608_ICHEP](https://github.com/RaoOfPhysics/201608_ICHEP)
</small>

</section>

---

<section><h1>Public engagement</h1>

##

- Conversation dominated with research fields that have:
    - direct impact
    - immediate impact

- What about fundamental research?

</section>

---

<section><h1>My PhD project</h1>

## "Engagement" &rarr; "Outreach"

- used to refer to all science-communication activities
“designed for an audience outside academia” (Crettaz&nbsp;von&nbsp;Roten, 2011, p.54)
- used among particle physicists to refer to:
    - working with schools
    - direct dialogue with the public
    - disseminating information through the media

##

> The term “outreach” refers to all science communication and education
activities that bring scientific research to audiences outside
the research community. It is also known as “popularisation”.

&mdash; note included in survey

## Research questions

- What are the attitudes towards outreach within the particle-physics
community and what are the motivations for and barriers against participating
- Do these vary w.r.t.
age, gender and academic position

## Research questions (…)

- How are these influenced by
    - funding bodies
    - national expectations towards outreach
    - the  multicultural nature of international collaborations
- How does the community perceive the usefulness and impact of outreach

</section>

---

<section data-background="images/1205187_03-A4-at-144-dpi.jpg">

##

### [CERN](http://home.cern)

The European Laboratory for Particle Physics

- Geneva, Switzerland
- host laboratory for international collaborations
- ~half of all 20,000 particle physicists

</section>

<section data-background="images/0910152_02-A4-at-144-dpi.jpg">

</section>

<section data-background="images/0807031_01-A4-at-144-dpi.jpg">

</section>

<section data-background="images/IMG_9286.JPG">

##

### The CMS Collaboration

[**C**ompact **M**uon **S**olenoid](http://cms.web.cern.ch)

- one of the two teams that [discovered the Higgs boson in 2012](http://cms.web.cern.ch/news/observation-new-particle-mass-125-gev)
- people (June 2015)
    - over 4000 physicists, engineers, students  (not including technicians
        and admin)
    - 183 institutes, universities, laboratories from 42 countries
    - 80+ nationalities

</section>

---

<section><h1>Data collection for quantitative analysis</h1>

## Electronic survey distributed by e-mail

- Sent to the whole collaboration via mailing list
- Three reminders sent to whole list
- Engineers reminded separately as well
- Representatives from low-response countries reminded separately

## Responses

- over 400, but a few duplicates
- final count: **391** valid responses
- ~10% of the collaboration

## CMS member countries

```{r}
# Code below by Rik Smith-Unna (@Blahah on GitHub)

# precompute the plot variable - this is required because we'll
# need to 'melt' the dataframe into long format, which will
# mix values from different variables in a column
countries$Country_Response_pc <-
    countries$Country_Response / countries$Country_Total * 100

# Some R wizardry I have yet to understand - Achintya
countries$Country <- factor(
    countries$Country,
    levels=arrange(countries, -Country_Response)$Country
    )

# select only the columns we need, then reshape
# the data frame by 'melting' it to long form.
# we only have one 'id variable' - country, so
# all the other variables will be collapsed
# into just two columns: variable and value
# we go from one row per country, to one row per value per country
# this is the format ggplot always uses - and it's super powerful
countries_long <- melt(
    countries[, c('Country', 'Country_Response', 'Country_Response_pc')],
    id=c('Country')
    )

# now just set x as country, but colour bars by another variable
p <- ggplot(countries_long, aes(x=Country, y=value, fill=variable)) +
    # we also need to specify that we want to use the values,
    # rather than the number of occurences, as the bar size
    # and that we want the bars side by side 'dodge' rather than
    # stacked
    geom_bar(stat='identity', position=position_dodge(), color="white") +
        coord_cartesian(ylim=c(0, 50))

ggplotly()

```
</section>

---

<section><h1>CONTENT</h1>


</section>

---

<section><h1>Conclusions</h1>

## CONCLUSIONS 1

## CONCLUSIONS 2

</section>

---

<section><h1>Acknowledgements</h1>

##

Emma Weitkamp, Clare Wilkinson, Erik Stengler, Christine Sutton, for supervising my research

Achille Petrilli, CMS Head of Communications, for supporting my research

Special thanks to Richard Smith-Unna (t: [\@blahah404](https://twitter.com/blahah404)) for help with R code!

##

[R](https://www.r-project.org/) + [RStudio](https://www.rstudio.com/)

[reveal.js](http://lab.hakim.se/reveal-js/)

[plotly](https://plot.ly/)

[RAW](http://raw.densitydesign.org/)

[Git](https://git-scm.com/) + [GitHub](https://github.com/)

</section>

# Thank you