---
title: "Support for participating in outreach and the benefits of doing so"
author: "Achintya Rao"
date: "6 August 2016"
output:
    revealjs::revealjs_presentation:
        theme: serif
        highlight: pygments
        incremental: true
        center: true
        transition: slide
        reveal_options:
            slideNumber: true
        fig_caption: true
        showNotes: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
dat <- read.csv(file = "../quant_analysis/final_dataset.csv", header = TRUE)
countries  <- read.csv(file = "data/countries.csv", header = TRUE)
library(dplyr)
library(plotly)
library(gridExtra)

# for long form conversion of data frame
library(reshape2)

likert_units <- seq(0.0000, 5.0000, by=1)
```

---

<section><h1>Conclusions</h1>

## Support for outreach participation

- SUPPORT 1
- SUPPORT 2

## Benefits of outreach participation

- BENEFIT 1
- BENEFIT 2

</section>

---

<section><h1>A bit about me</h1>

##

> - **Science Communicator** (2010 &mdash; present)<br />Compact Muon Solenoid
(CMS) Collaboration at CERN
> - **Doctoral Student** (2014 &mdash; present)<br />UWE Science Communication
Unit, Bristol
>     - **MA in Science Journalism** (2009 &mdash; 2010)<br />City University,
London
>     - **BSc in Physics** (2005 &mdash; 2008)<br />St. Xavier’s College,
Mumbai (Bombay)

<br />
<br />
<small>
Twitter: [\@RaoOfPhysics](https://twitter.com/RaoOfPhysics) |
GitHub: [\@RaoOfPhysics](https://github.com/RaoOfPhysics)<br />
This presentation: [github.com/RaoOfPhysics/201608_ICHEP](https://github.com/RaoOfPhysics/201608_ICHEP)
</small>

</section>

---

<section><h1>Science Communication: Evolving Views</h1>

## Scientific Literacy

“greater knowledge about the facts of science will  improve people’s lives while gaining public support for, and reducing opposition to, research”

##  Public Understanding of Science and Technology

> “part of each scientist’s professional responsibility  to promote the public understanding of science”

&mdash; The Royal Society, 1985

## The Deficit Model

“the role of scientists and science communicators is to fill a perceived knowledge deficit among the public”

## Low levels of Scientific Literacy

> “Many [scientists] recognise, in their own inability to be certain of their answers, that the public cannot be expected to retain  facts that are not useful.”

&mdash; Stocklmayer & Bryant, 2012

</section>

---

<section><h1>Public Engagement with Science and Technology</h1>

> “while scientists may have scientific facts at their disposal, the members of the public concerned have local knowledge and an understanding of, and personal interest in, the problems to be solved”

&mdash; Miller, 2001

## Three aspects/stages:

> 1. “scientists […] encouraged to inform the public”
> 2. “scientists […] encouraged to develop dialogue on scientific facts and processes”
> 3. “scientists must engage with society in the early phase of scientific development”

&mdash; Crettaz von Roten, 2011

## Science Communication research

- Conversation dominated with research fields that have:
    - direct impact
    - immediate impact

- What about fundamental research?

</section>

---

<section><h1>My PhD project</h1>

## "Engagement" &rarr; "Outreach"

- used to refer to all science-communication activities
“designed for an audience outside academia” (Crettaz&nbsp;von&nbsp;Roten, 2011, p.54)
- used among particle physicists to refer to:
    - working with schools
    - direct dialogue with the public
    - disseminating information through the media

##

> The term “outreach” refers to all science communication and education
activities that bring scientific research to audiences outside
the research community. It is also known as “popularisation”.

&mdash; note included in survey

## Research questions

- What are the attitudes towards outreach within the particle-physics
community and what are the motivations for and barriers against participating
- Do these vary w.r.t.
age, gender and academic position

## Research questions (…)

- How are these influenced by
    - funding bodies
    - national expectations towards outreach
    - the multicultural nature of international collaborations
- How does the community perceive the usefulness and impact of outreach

</section>

---

<section data-background="images/1205187_03-A4-at-144-dpi.jpg">

##

### [CERN](http://home.cern)

The European Laboratory for Particle Physics

- Geneva, Switzerland
- host laboratory for international collaborations
- ~half of all 20,000 particle physicists

</section>

<section data-background="images/0910152_02-A4-at-144-dpi.jpg">

</section>

<section data-background="images/0807031_01-A4-at-144-dpi.jpg">

</section>

<section data-background="images/IMG_9286.JPG">

##

### The CMS Collaboration

[**C**ompact **M**uon **S**olenoid](http://cms.web.cern.ch)

- one of the two teams that [discovered the Higgs boson in 2012](http://cms.web.cern.ch/news/observation-new-particle-mass-125-gev)
- people (June 2015)
    - over 4000 physicists, engineers, students  (not including technicians
        and admin)
    - 183 institutes, universities, laboratories from 42 countries
    - 80+ nationalities

</section>

---

<section><h1>Data collection for quantitative analysis</h1>

## Electronic survey distributed by e-mail

- Sent to the whole collaboration via mailing list
- Three reminders sent to whole list
- Engineers reminded separately as well
- Representatives from low-response countries reminded separately

## Responses

- over 400, but a few duplicates
- final count: **391** valid responses
- ~10% of the collaboration

## CMS member countries

```{r}
# Code below by Rik Smith-Unna (@Blahah on GitHub)

# precompute the plot variable - this is required because we'll
# need to 'melt' the dataframe into long format, which will
# mix values from different variables in a column
countries$Country_Response_pc <-
    countries$Country_Response / countries$Country_Total * 100

# Some R wizardry I have yet to understand - Achintya
countries$Country <- factor(
    countries$Country,
    levels=arrange(countries, -Country_Response)$Country
    )

# select only the columns we need, then reshape
# the data frame by 'melting' it to long form.
# we only have one 'id variable' - country, so
# all the other variables will be collapsed
# into just two columns: variable and value
# we go from one row per country, to one row per value per country
# this is the format ggplot always uses - and it's super powerful
countries_long <- melt(
    countries[, c('Country', 'Country_Response', 'Country_Response_pc')],
    id=c('Country')
    )

# now just set x as country, but colour bars by another variable
p <- ggplot(countries_long, aes(x=Country, y=value, fill=variable)) +
    # we also need to specify that we want to use the values,
    # rather than the number of occurences, as the bar size
    # and that we want the bars side by side 'dodge' rather than
    # stacked
    geom_bar(stat='identity', position=position_dodge(), color="white") +
        coord_cartesian(ylim=c(0, 50))

ggplotly()

```
</section>

---

<section><h1>Support for outreach participation</h1>

##

```{r}
imp_because_taxes <- melt(as.matrix(dat[c('imp_because_taxes')]))
imp_because_taxes$value <- factor(imp_because_taxes$value, 
                                  levels=c(1, 2, 3, 4, 5))

ggplot(imp_because_taxes, aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    theme_bw() +
    labs(title = "“It is important for scientists to take part in outreach activities \nbecause taxes from citizens fund research.”")
```

*… outreach is important because research is supported by taxes…*

##

```{r}
funding_should_support <- melt(as.matrix(dat[c('funding_should_support')]))
funding_should_support$value <- factor(funding_should_support$value, 
                                       levels=c(1, 2, 3, 4, 5))

ggplot(funding_should_support, aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    theme_bw() +
    labs(title = "““Funding bodies should provide support for scientists \nto communicate their research to the non-specialist public.”")
```

*… funding bodies should scientists help do outreach…*

##

```{r}
grants_wider_society <- melt(as.matrix(dat[c('grants_wider_society')]))
grants_wider_society$value <- factor(grants_wider_society$value, 
                                     levels=c(1, 2, 3, 4, 5))

ggplot(grants_wider_society, aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    theme_bw() +
    labs(title = "“When applying for grants, scientists should be required to provide details \non how their research will be communicated to the wider society.”")
```

*… outreach details included in grant applications…*

</section>

---

<section><h1>Benefits of outreach participation</h1>

##

```{r}
attracts_funding <- melt(as.matrix(dat[c('attracts_funding')]))
attracts_funding$value <- factor(attracts_funding$value, 
                                 levels=c(1, 2, 3, 4, 5))

ggplot(na.omit(attracts_funding), aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    theme_bw() +
    labs(title = "“[Participating in outreach] attracts research funding.”")
```

*… attracts research funding…*

##

```{r}
advances_career <- melt(as.matrix(dat[c('advances_career')]))
advances_career$value <- factor(advances_career$value, 
                                levels=c(1, 2, 3, 4, 5))

ggplot(na.omit(advances_career), aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    theme_bw() +
    labs(title = "“[Participating in outreach] advances my career.”")
```

*… advances my career…*

##

```{r}
makes_better_scientist <- melt(as.matrix(dat[c('makes_better_scientist')]))
makes_better_scientist$value <- factor(makes_better_scientist$value, 
                                       levels=c(1, 2, 3, 4, 5))

ggplot(na.omit(makes_better_scientist), aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    theme_bw() +
    labs(title = "“[Participating in outreach] makes me a better scientist.”")
```

*… makes me a better scientist…*

##

```{r}
collaboration_opportunities <-
    melt(as.matrix(dat[c('collaboration_opportunities')]))
collaboration_opportunities$value <- factor(collaboration_opportunities$value, 
                                            levels=c(1, 2, 3, 4, 5))

ggplot(na.omit(collaboration_opportunities), aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    theme_bw() +
    labs(title = "“[Participating in outreach] is an opportunity for others \nto contact me for collaborative purposes.”")
```

*… collaboration opportunities…*

##

```{r}
research_new_ways <- melt(as.matrix(dat[c('research_new_ways')]))
research_new_ways$value <- factor(research_new_ways$value, 
                                  levels=c(1, 2, 3, 4, 5))

ggplot(na.omit(research_new_ways), aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    theme_bw() +
    labs(title = "“[Participating in outreach] shapes the direction of my research \nand makes me think about it in new ways.”")
```

*… think of my research in new ways…*

##

```{r}
feeling_enjoyment <- melt(as.matrix(dat[c('feeling_enjoyment')]))
feeling_enjoyment$value <- factor(feeling_enjoyment$value, 
                                  levels=c(1, 2, 3, 4, 5))

ggplot(na.omit(feeling_enjoyment), aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    theme_bw() +
    labs(title = "“I get a feeling of enjoyment \n[from participating in outreach].”")
```

*… feeling of enjoyment…*

##

```{r}
job_satisfaction <- melt(as.matrix(dat[c('job_satisfaction')]))
job_satisfaction$value <- factor(job_satisfaction$value, 
                                 levels=c(1, 2, 3, 4, 5))

ggplot(na.omit(job_satisfaction), aes(x = value)) + 
    geom_bar(stat="count", colour="white") + 
    geom_text(stat="count", aes(label = ..count..,
                                y=..count..), vjust=-0.5) +
    scale_x_discrete(name = NULL,
                     limits = c(1:5), 
                     drop = FALSE, 
                     labels = c("1" = "1\nStrongly Disagree",
                                "2" = "2", "3" = "3", "4" = "4", 
                                "5" = "5\nStrongly Agree")) +
    
    ylab("Count") +
    theme_bw() +
    labs(title = "“[Participating in outreach] gives me job satisfaction.”")
```

*… job satisfaction…*

</section>

---

<section><h1>Conclusions</h1>

## CONCLUSIONS 1

## CONCLUSIONS 2

</section>

---

<section><h1>Acknowledgements</h1>

##

Emma Weitkamp, Clare Wilkinson, Erik Stengler, Christine Sutton, for supervising my research

Achille Petrilli, CMS Head of Communications, for supporting my research

Special thanks to Richard Smith-Unna (t: [\@blahah404](https://twitter.com/blahah404)) for help with R code!

##

[R](https://www.r-project.org/) + [RStudio](https://www.rstudio.com/)

[reveal.js](http://lab.hakim.se/reveal-js/)

[plotly](https://plot.ly/)

[RAW](http://raw.densitydesign.org/)

[Git](https://git-scm.com/) + [GitHub](https://github.com/)

</section>

# Thank you